---
title: "Chapter 9 - functionals pt2"
author: "Ian"
date: "2023-02-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library("purrr")
```

```{r}
l <- map(1:4, ~ sample(1:10, 15, replace = T))
str(l)
#> List of 4
#>  $ : int [1:15] 7 1 8 8 3 8 2 4 7 10 ...
#>  $ : int [1:15] 3 1 10 2 5 2 9 8 5 4 ...
#>  $ : int [1:15] 6 10 9 5 6 7 8 6 10 8 ...
#>  $ : int [1:15] 9 8 6 4 4 5 2 9 9 6 ...
#>  
```

### 9.6.3 Exercises
1) Why isn’t is.na() a predicate function? What base R function is closest to being a predicate version of is.na()? simple_reduce() has a problem when x is length 0 or length 1. Describe the source of the problem and how you might go about fixing it.

predicate functions return a `TRUE` or a `FALSE` while `is.na()` returns a logical. `anyNA()` 

2) Use Filter() and vapply() to create a function that applies a summary statistic to every numeric column in a data frame
```{r}
vapply_num <- function(X, FUN, FUN.VALUE){
  vapply(Filter(is.numeric, X), FUN, FUN.VALUE)
}

```
3) What’s the relationship between which() and Position()? What’s the relationship between where() and Filter()?
```{r}
where <- function(f, x) {
  vapply(x, f, logical(1))
} 
```

```
simple_reduce <- function(x, f) {
  out <- x[[1]]
  for (i in seq(2, length(x))) {
    out <- f(out, x[[i]])
  }
  out
}
```
Implement the span() function from Haskell: given a list x and a predicate function f, span(x, f) returns the location of the longest sequential run of elements where the predicate is true. (Hint: you might find rle() helpful.)

Implement arg_max(). It should take a function and a vector of inputs, and return the elements of the input where the function returns the highest value. For example, arg_max(-10:5, function(x) x ^ 2) should return -10. arg_max(-5:5, function(x) x ^ 2) should return c(-5, 5). Also implement the matching arg_min() function.

The function below scales a vector so it falls in the range [0, 1]. How would you apply it to every column of a data frame? How would you apply it to every numeric column in a data frame?