---
title: "Chapter 9 - functionals pt2"
author: "Ian"
date: "2023-02-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library("purrr")
```

```{r}
l <- map(1:4, ~ sample(1:10, 15, replace = T))
str(l)
#> List of 4
#>  $ : int [1:15] 7 1 8 8 3 8 2 4 7 10 ...
#>  $ : int [1:15] 3 1 10 2 5 2 9 8 5 4 ...
#>  $ : int [1:15] 6 10 9 5 6 7 8 6 10 8 ...
#>  $ : int [1:15] 9 8 6 4 4 5 2 9 9 6 ...
#>  
```

### 9.6.3 Exercises
1) Why isn’t is.na() a predicate function? What base R function is closest to being a predicate version of is.na()? simple_reduce() has a problem when x is length 0 or length 1. Describe the source of the problem and how you might go about fixing it.

predicate functions return a `TRUE` or a `FALSE` while `is.na()` returns a logical. `anyNA()` 

2) Use Filter() and vapply() to create a function that applies a summary statistic to every numeric column in a data frame
```{r}
vapply_num <- function(X, FUN, FUN.VALUE){
  vapply(Filter(is.numeric, X), FUN, FUN.VALUE)
}

```
3) What’s the relationship between which() and Position()? What’s the relationship between where() and Filter()?
```{r}
where <- function(f, x) {
  vapply(x, f, logical(1))
} 
```


3_version2) Implement the span() function from Haskell: given a list x and a predicate function f, span(x, f) returns the location of the longest sequential run of elements where the predicate is true. (Hint: you might find rle() helpful.)
```{r}

span <- function(x, f) {
  idx <- unname(map_lgl(x, ~ f(.x)))
  rle <- rle(idx) 
  if (!any(rle$values)) {
    return(integer(0))
  }
  longest <- max(rle$lengths[rle$values])
  longest_idx <- which(rle$values & rle$lengths == longest)[1]
  ind_before_longest <- sum(rle$lengths[seq_len(longest_idx - 1)])
  out_start <- ind_before_longest + 1L
  out_end <- ind_before_longest + longest
  out_start:out_end
}
span(c(0,  0,  0,  0,  0), is.na)
span(c(NA, 0,  0,  0,  0), is.na)
span(c(NA, 0, NA, NA, NA), is.na)
```


4) implement arg_max(). It should take a function and a vector of inputs, and return the elements of the input where the function returns the highest value. For example, arg_max(-10:5, function(x) x ^ 2) should return -10. arg_max(-5:5, function(x) x ^ 2) should return c(-5, 5). Also implement the matching arg_min() function.

```{r}
arg_max <- function(x, f) {
  y <- map_dbl(x, f)
  #print(y)
  x[y == max(y)]
}
arg_min <- function(x, f) {
  y <- map_dbl(x, f)
  x[y == min(y)]
}
arg_max(-10:5, function(x) x ^ 2)
arg_min(-10:5, function(x) x ^ 2)
```


```{r}
fixed_point_algorithm <- function(f, x0, tol=1e-8, max_iter=1000) {
  x_old <- x0
  for (i in 1:max_iter) {
    x_new <- f(x_old)
    if (abs(x_new - x_old) < tol) {
      return(x_new)
    }
    x_old <- x_new
  }
  return(x_new)
}
fixed_point_algorithm(function(x) x^2, c(3,3,5))
```